Simulation of Nano Particles in a Laser Trap

### 2017-01-27 doc/draft2.tex
much changes
achtung! geschwindigkeits-initialisierung geaendert!

This means that the particle number $N$, the volume $V$ and the
total energy $E$ are constant. In contrast to the NVT ensemble used in Monte-Carlo simulations this means, that the velocities of the particle can not
be chosen directly. The initial velocities have to be drawn from a random number generator. This means that the velocities have to be adjusted after 
they have been drawn.\\

@@

of all the atoms in the system have to be added to get the resulting velocity vector for the whole system that is thought to be acting on the center
of mass. This resulting vector is then divided by the number of particles in the system and the resulting vector is then subtracted from every

@@

@@

\\The velocities of the particle can roughly be chosen by adjusting the range of numbers the random number generator can choose from. However, the
resulting velocities (and therefore the temperature of the system) are generally not precisely how they should be. If the system should have a

@@

This process has to be done a couple of times, until the system equilibrates to the desired temperature. The problem with this procedure is the fact
that it contradicts the constant energy property of the ensemble. If we look at the energy values in Fig.~\ref{fig:energystart} we can see the

>>>>

This means that the particle number $N$, the volume $V$ and the total energy $E$ are constant. 
The initial velocities of the particles are chosen randomly from a Maxwell-Boltzmann distribution. To ensure that the system behaves the way it is
intended to, small adjustments have to be made in the beginning of the simulation of the nano particle.\\
%In contrast to the NVT ensemble used in Monte-Carlo simulations this means, that the velocities of the particle can not
%be chosen directly. The initial velocities have to be drawn from a random number generator. This means that the velocities have to be adjusted after 
%they have been drawn.\\

@@

of all the atoms in the system have to be added to get the resulting velocity vector for the whole system. 
This resulting vector is then divided by the number of particles in the system and the resulting vector is then subtracted from every

@@

This adjustment only needs to be done just after randomly choosing the velocities, as there is no force present at this point that would cause the
nano particle to move.

@@

%\\The velocities of the particle can roughly be chosen by adjusting the range of numbers the random number generator can choose from. However, the
%resulting velocities (and therefore the temperature of the system) are generally not precisely how they should be. 
\\As mentioned above, the velocities are chosen from a Maxwell-Boltzmann distribution, which means choosing each component from a Gaussian
distribution. However, the positions on the FCC lattice are not very natural and so the atoms equilibrate to a different temperature than desired.
If the system should have a

@@

This process has to be done a couple of times, until the system equilibrates to the desired temperature. 
%The problem with this procedure is the fact
%that it is not compatible with the requirement of constant energy of the system. 
If we look at the energy values in Fig.~\ref{fig:energystart} we can see the
